Pillar 2 - Topic Modeling

### 2019-01-11 Pillar 2 - Topic Modeling.Rmd
functions prepare_tf_idf_

```{r function make_barplot and make_WC, out.height=8, out.width=16}
plot_tf_idf <- function(data, facet = Course, top = 10, n_col = 5, plot_id = NULL){

  # Setup
  facet_enquo <- enquo(facet)
  facet_ensym <- ensym(facet)

  # Data

  data <- 
    if(facet_ensym == sym("Course")) data %>%
      filter(Code %in% sample(unique(.$Code), size = n_col^2, replace = F)) %>% # random selection of courses
      rename(facet = Code) %>%
      group_by(facet) %>%
      filter(n >= 2) %>%
      top_n(top, tf_idf) %>%
      ungroup

    else if(facet_ensym == sym("Cluster")) data %>%
      left_join(data, select(d_course, Code, Cluster), by = "Code") %>%
      rename(facet = !!facet_enquo) %>%
      group_by(facet) %>%
      summarise(tf_idf = sum(tf_idf))
      filter(n >= 10) %>%
      top_n(top, tf_idf) %>%
      ungroup

      return(data)

@@

    ggsave(paste(plot_id, facet_ensym, "_BP.jpeg", sep = ""), path = "Plots", width = 16, height = 8)
    print(g)

@@

  ggsave(paste(plot_id, facet_ensym, "_WC.jpeg", sep = ""), path = "Plots", width = 16, height = 8)
  print(g)

@@

## Course Level
```{r tf-idf per course, out.height=8, out.width=16}
set.seed(123)
plot_tf_idf(tf_idf_description, plot_id = "description_")
set.seed(123)
plot_tf_idf(tf_idf_overview, plot_id = "overview_")
set.seed(123)
plot_tf_idf(tf_idf_manual, plot_id = "manual_")
```

## Cluster Level
```{r tf-idf per cluster}

tdm_top <- d_overview_stem %>%
  left_join(select(d_course, Code, Cluster), by = "Code") %>%
  filter(`Calendar Year` == "2018-2019",
         !is.na(Cluster)) %>%
  count(Cluster, `Calendar Year`, word, sort = T) %>%
  bind_tf_idf(term = word, document = Cluster, n = n) %>%
  filter(n >= 5) %>%
  group_by(Cluster) %>%
  top_n(10, tf_idf) %>%
  ungroup

# Plots
make_barplot(data = tdm_top, facet = Cluster, n_col = 4)
make_WC(data = tdm_top, facet = Cluster, n_col = 4)
```

>>>>

```{r function make_barplot and make_WC, out.height=8, out.width=16}
plot_tf_idf <- function(data, top = 10, n_col = 5, plot_id = NULL){

@@

  ggsave(paste(plot_id, "_BP.jpeg", sep = ""), path = "Plots", width = 16, height = 8)
  print(g)

@@

  ggsave(paste(plot_id, "_WC.jpeg", sep = ""), path = "Plots", width = 16, height = 8)
  print(g)

@@

## Course Level
```{r tf-idf per course, out.height=8, out.width=16}
prepare_tf_idf_course <- function(data) data %>%
                                          filter(Code %in% sample(unique(.$Code), size = 25, replace = F)) %>% # random selection of courses
                                          rename(facet = Code) %>%
                                          group_by(facet) %>%
                                          filter(n >= 2) %>%
                                          top_n(10, tf_idf) %>%
                                          ungroup

set.seed(123)
tf_idf_description %>%
  prepare_tf_idf_course %>%
  plot_tf_idf(plot_id = "Course_description")

set.seed(123)
tf_idf_overview %>%
  prepare_tf_idf_course %>%
  plot_tf_idf(plot_id = "Course_overview")

set.seed(123)
tf_idf_manual %>%
  prepare_tf_idf_course %>%
  plot_tf_idf(plot_id = "Course_manual")
```

## Cluster Level
```{r tf-idf per cluster}
prepare_tf_idf_cluster <- function(data) data %>%
                                           left_join(select(d_course, Code, Cluster), by = "Code") %>%
                                           filter(!is.na(Cluster)) %>%
                                           rename(facet = Cluster) %>%
                                           group_by(facet, word) %>%
                                             summarise(tf_idf = sum(tf_idf),
                                                       n = sum(n)) %>%
                                             filter(n >= 10) %>%
                                             top_n(10, tf_idf) %>%
                                           ungroup

tf_idf_description %>%
  prepare_tf_idf_cluster %>%
  plot_tf_idf(plot_id = "Cluster_description")

tf_idf_overview %>%
  prepare_tf_idf_cluster %>%
  plot_tf_idf(plot_id = "Cluster_overview")

tf_idf_manual %>%
  prepare_tf_idf_cluster %>%
  plot_tf_idf(plot_id = "Cluster_manual")
```
